{\fontfamily{ptm}\selectfont Nesterov Type Momentum Methods}

### 2024-07-04 Notebook LaTEX/Momentum Accelerations/main.tex
>w< new notes updated

    \subsection{Preliminaries}
        We introduce some additional lemma that are crucial to the derivations of non-smooth accelerated gradient method. 
        \begin{definition}[The Gradient Mapping]
            \label{def:gradient_mapping}
            Let $g = f + g$ where $f$ is $L$-Lipschitz smooth and convex, $g$ is convex. 
            Define the proximal gradient operator
            $$
                \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
            $$
            then the gradient mapping is defined as
            $$
                \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
            $$
        \end{definition}
        \begin{remark}
            The name "gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing. 
        \end{remark}

@@

        \begin{lemma}[Linearized Gradient Mapping Lower Bound]
        \label{lemma:grad_map_linearization}
            Continue from 
            \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
            with $x^+ = \mathcal T(x)$, the gradient mapping satisfies the inequality for all $z$: 
            \begin{align*}
                h(z) &\ge
                h(z) - \frac{L}{2}\Vert x - x^+\Vert^2
                \ge h(x^+) + \langle \mathcal G_L(x), z - x\rangle. 
            \end{align*}
        \end{lemma}
        \begin{proof}
            Directly from the $L$-smoothness of $f$, convexity of $g, f$, we have the list of inequalities: 
            \begin{align*}
                &f(x^+) \le 
                f(x) + \langle \nabla f(x), x^+ - x\rangle
                + \frac{L}{2}\Vert x - x^+\Vert^2, 
                \\
                &f(x) + \langle \nabla f(x), z - x\rangle 
                \le f(z), 
                \\
                &g(x^+) \le 
                g(z) + \langle \partial g(x^+), x^+ - z\rangle. 
            \end{align*}
            Now, consider adding $g(x^+)$ to the first inequality from above we get 
            {\footnotesize 
            \begin{align*}
                f(x^+) + g(x^+) 
                &\le 
                f(x) + g(x^+) + \langle \nabla f(x), x^+ - x\rangle 
                + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &\le 
                (f(z) - \langle \nabla f(x), z - x\rangle) + 
                \left(g(z) - \langle \partial g(x^+), x^+ - z\rangle\right)
                + 
                \langle \nabla f(x), x^+ - x\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= f(z) + g(z) + \langle \nabla f(x), x - z + x^+ - x\rangle
                + 
                \langle \partial g(x^+), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= 
                h(z) + \langle \nabla f(x), x^+ - z\rangle + 
                \langle \partial g(x^+), x^+ - z\rangle
                + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= h(z) + \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 
                + \frac{L}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            }
            By $\mathcal G_L(x) = L(x - x^+) \in \nabla f(x) + \partial g(x^+)$ from previous dicussion, we have 
            \begin{align*}
                h(x^+) &\le 
                h(z) + \langle \mathcal G_L(x), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= h(z) - \langle L(x^+ - x), x^+ - x + x - z \rangle 
                + 
                \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= 
                h(z) - L\Vert x^+ - x\Vert^2 
                + L \langle x^+ - x, x - z\rangle
                + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= h(z) + \langle \mathcal G_L(x), x - z\rangle - 
                \frac{L}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Therefore, the inequality is justified. 
        \end{proof}
        \begin{remark}
            Observe that the linearization $h(x^+) + \langle \mathcal G_L(x), z - x\rangle$ is anchored at $x^+$, instead of $x$. 
            Geometrically, it's tilted and it "prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
        \end{remark}

@@

            \begin{definition}[AG Proximal Gradient PPM Generic Form]
            \label{def:ag_prox_grad_ppm}
                Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
                Define the proximal gradient and gradient mapping operator operator: 
                $$
                \begin{aligned}
                    \mathcal T_L^{g, f}(x) &:=  
                    \hprox_{L^{-1}g}\left(x - L^{-1}\nabla f(x)\right)
                    \\
                    &= 
                    \argmin_{u}
                    \left\lbrace
                        g(u) + f(x) + \langle \nabla f(x), u - x\rangle
                        + 
                        \frac{L}{2}\Vert u - x\Vert^2
                    \right\rbrace,
                    \\
                    \mathcal G_L^{g, f}(x) &= 
                    L(x - \mathcal T_L^{g, f}(x)). 
                \end{aligned}
                $$
                Omitting the superscript $f, g$ on $\mathcal P, \mathcal G$ for simplicity since it's clear in the context. 
                Define the linear lower bounding function for $f$ at $y$, for all $x$: 
                $$
                \begin{aligned}
                    l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle \le f(x), 
                \end{aligned}
                $$
                With that we define the algorithm:
                $$
                \begin{aligned}
                    x_{t + 1} &= \argmin_{x} \left\lbrace
                        l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                        \Vert x - x_t\Vert^2
                    \right\rbrace,
                    \\
                    y_{t + 1}&= 
                    \argmin_{x}
                    \left\lbrace
                        g(x) + l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                        \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
                    \right\rbrace.
                \end{aligned}
                $$
            \end{definition}

            \begin{definition}[Tri-points Generic Form]\label{def:agg_tri}
                With $f$ be $L$-Lipschitz \\ 
                smooth and convex, choose any $y_0 = x_0=z_0$ and a non-negative sequence $\eta_t, \tilde\eta_t$, the algorithm admits form: 
                \begin{align*}
                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
                    \\
                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
                    \\
                    y_{t + 1} &= 
                    (1 + L\eta_{t + 1})^{-1}
                    (
                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                    ). 
                \end{align*}
            \end{definition}
            \begin{remark}
                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra (6.24), but with the choice of $\mu = 0$. 
                This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
                They are the same parameters for both algorithms and they are equivalent. 
                This will be proved in the coming parts. 
            \end{remark}
            \begin{definition}[Strongly Convex Tri-points Generic Form]
                \quad 
                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex Tri-Points generic form has updates of for iterates
                \begin{align*}
                    x_{t + 1} &= (1 + \mu\tilde \eta_{t + 1})^{-1}(x_t + \mu\tilde\eta_{t + 1}y_t^+), 
                    \\
                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), 
                    \\
                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L\eta_{t + 1}z_{t +1}). 
                \end{align*}
            \end{definition}

        \subsubsection*{Useful Observations about these Generic forms}\label{sec:AG_useful_information}

@@

            \begin{proposition}[Tripoints Strongly Convex Form via Ahn Sra 6.24]\label{prop:tri_scvx_from_ahn_sra_6.24}
                Coninue \\ 
                from \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with but with $\mu > 0$, under the same set of assumptions it recovers a tri-points algorithm with the following updates: 
                \begin{align*}
                    y_t^+ &= y_t - \mu^{-1}\nabla f(y_t)
                    \\
                    x_{t + 1} &= \argmin_{x} 
                    \left\lbrace
                        l_f (x; y_t) + \frac{\mu}{2} \Vert x - y_t\Vert^2 + 
                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2 
                    \right\rbrace
                    \\
                    &= \argmin_{x}
                    \left\lbrace
                        f(y_t) - \frac{1}{2\mu} \Vert \nabla f(y_t)\Vert^2 
                        + 
                        \frac{\mu
                        }{2}\Vert x - y_t^+\Vert^2
                        + 
                        \frac{1}{2\tilde \eta_{t + 1}}\Vert x - x_t\Vert^2
                    \right\rbrace
                    \\
                    &= (1 + \mu\tilde \eta_{t + 1})^{-1}
                    \left(
                        x_t + \mu \tilde \eta_{t + 1}y_t^{+}
                    \right)
                    \\
                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
                    \\
                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L \eta_{t + 1} z_{t + 1})
                \end{align*}
            \end{proposition}
            \begin{proof}
                By a similar argument made in the remarks of \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}} we have 
                \begin{align*}
                    l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2
                    &= 
                    f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
                    \\
                    \implies 
                    x_{t + 1} &= 
                    \argmin_{x} 
                    \left\lbrace
                        f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
                        + 
                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
                    \right\rbrace
                    \\
                    &= 
                    \argmin_{x}
                    \left\lbrace
                        \frac{\mu}{2}\Vert x - y_t^+\Vert^2 + 
                        \frac{2}{\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
                    \right\rbrace
                    \\
                    &= (\mu + \tilde \eta_{t + 1})^{-1}
                    (\mu y_t^+ + \tilde \eta_{t + 1}x_t)
                    \\
                    &= (1 + \tilde \eta_{t + 1}\mu)^{-1}
                    (x_t + \mu\tilde \eta_{t + 1}y_t^+). 
                \end{align*}
                The updates for $y_{t + 1}, z_{t + 1}$ is the same as before because $\mu > 0$ only alters the update of the term $x_{t + 1}$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
            \end{proof}

@@

            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} and \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} then these are the upper bounds for the RHS of the PPM descent inequality: 
                \Upsilon_{1, t + 1}^{\text{AG}}&= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))

@@

@@

            In this remark we clarify the name "similar triangule" as given in the literatures. 

>>>>

    \subsection{Preliminaries}
        We introduce some additional lemma that are crucial to the derivations of non-smooth accelerated gradient method. 
        \begin{definition}[The Gradient Mapping]
            \label{def:gradient_mapping}
            Let $g = f + g$ where $f$ is $L$-Lipschitz smooth and convex, $g$ is convex. 
            Define the proximal gradient operator
            $$
                \mathcal T_L(x) := \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)),
            $$
            then the gradient mapping is defined as
            $$
                \mathcal G_L(x) = L(x - \mathcal T_L(x)). 
            $$
        \end{definition}
        \begin{remark}
            The name ``gradient mapping" comes from \cite[(2.2.54)]{nesterov_lectures_2018}, however, Nesterov was referring to only the case when $g$ is an indicator function of a convex set in his writing. 
            Of course, in Amir Beck \cite[10.3.2]{beck_first-order_nodate}, it has the exact same definition for gradient mapping as the above. 
        \end{remark}

@@

        \begin{lemma}[Linearized Gradient Mapping Lower Bound]
        \label{lemma:grad_map_linearization}
            Continue from 
            \hyperref[lemma:grad_map_lemma_first]{definition \ref*{lemma:grad_map_lemma_first}}, 
            with $x^+ = \mathcal T_L(x)$, the gradient mapping satisfies the inequality for all $z$: 
            \begin{align*}
                h(z) &\ge
                h(z) - \frac{L}{2}\Vert x - x^+\Vert^2
                \ge h(x^+) + \langle \mathcal G_L(x), z - x\rangle. 
            \end{align*}
        \end{lemma}
        \begin{proof}
            Directly from the $L$-smoothness of $f$, convexity of $g, f$, we have the list of inequalities: 
            \begin{align*}
                &f(x^+) \le 
                f(x) + \langle \nabla f(x), x^+ - x\rangle
                + \frac{L}{2}\Vert x - x^+\Vert^2, 
                \\
                &f(x) + \langle \nabla f(x), z - x\rangle 
                \le f(z), 
                \\
                &g(x^+) \le 
                g(z) + \langle \partial g(x^+), x^+ - z\rangle. 
            \end{align*}
            Now, consider adding $g(x^+)$ to the first inequality from above we get 
            {\footnotesize 
            \begin{align*}
                f(x^+) + g(x^+) 
                &\le 
                f(x) + g(x^+) + \langle \nabla f(x), x^+ - x\rangle 
                + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &\le 
                (f(z) - \langle \nabla f(x), z - x\rangle) + 
                \left(g(z) - \langle \partial g(x^+), x^+ - z\rangle\right)
                + 
                \langle \nabla f(x), x^+ - x\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= f(z) + g(z) + \langle \nabla f(x), x - z + x^+ - x\rangle
                + 
                \langle \partial g(x^+), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= 
                h(z) + \langle \nabla f(x), x^+ - z\rangle + 
                \langle \partial g(x^+), x^+ - z\rangle
                + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= h(z) + \langle \nabla f(x) + \partial g(x^+), x^+ - z\rangle 
                + \frac{L}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            }
            By $\mathcal G_L(x) = L(x - x^+) \in \nabla f(x) + \partial g(x^+)$ from previous dicussion, we have 
            \begin{align*}
                h(x^+) &\le 
                h(z) + \langle \mathcal G_L(x), x^+ - z\rangle + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= h(z) - \langle L(x^+ - x), x^+ - x + x - z \rangle 
                + 
                \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= 
                h(z) - L\Vert x^+ - x\Vert^2 
                + L \langle x^+ - x, x - z\rangle
                + \frac{L}{2}\Vert x - x^+\Vert^2
                \\
                &= h(z) + \langle \mathcal G_L(x), x - z\rangle - 
                \frac{L}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Therefore, the inequality is justified. 
        \end{proof}
        \begin{remark}
            Observe that the linearization $h(x^+) + \langle \mathcal G_L(x), z - x\rangle$ is anchored at $x^+$, instead of $x$. 
            Geometrically, it's tilted and it "prefers" the sharp corners of a convex function, if, $x$ is close to a sharp corner. 
        \end{remark}

@@

            \begin{definition}[AG Proximal Gradient PPM Generic Form]
            \label{def:ag_prox_grad_ppm}
                Let $h=f + g$ be the sum of convex function $g$ and convex differentiable $f$ with $L$-Lipschitz gradient. 
                Define the proximal gradient and gradient mapping operator operator: 
                $$
                \begin{aligned}
                    \mathcal T_L^{g, f}(x) &:=  
                    \hprox_{L^{-1}g}\left(x - L^{-1}\nabla f(x)\right)
                    \\
                    &= 
                    \argmin_{u}
                    \left\lbrace
                        g(u) + f(x) + \langle \nabla f(x), u - x\rangle
                        + 
                        \frac{L}{2}\Vert u - x\Vert^2
                    \right\rbrace,
                    \\
                    \mathcal G_L^{g, f}(x) &= 
                    L\left(x - \mathcal T_L^{g, f}(x)\right). 
                \end{aligned}
                $$
                Omitting the superscript $f, g$ on $\mathcal P, \mathcal G$ for simplicity since it's clear in the context. 
                Define the linear lower bounding function for $f$ at $y$, for all $x$: 
                $$
                \begin{aligned}
                    l_h(x; y) &= h(\mathcal T_L y) + \langle \mathcal G_L(y), x - y \rangle \le f(x), 
                \end{aligned}
                $$
                With that we define the algorithm:
                $$
                \begin{aligned}
                    x_{t + 1} &= \argmin_{x} \left\lbrace
                        l_h(x; y_t) + \frac{1}{2\tilde \eta_{t + 1}} 
                        \Vert x - x_t\Vert^2
                    \right\rbrace,
                    \\
                    y_{t + 1}&= 
                    \argmin_{x}
                    \left\lbrace
                        g(x) + l_f(x; y_t) + \frac{L}{2}\Vert x - y_t\Vert^2 + 
                        \frac{1}{2\eta_{t + 1}} \Vert x - x_{t + 1}\Vert^2
                    \right\rbrace.
                \end{aligned}
                $$
            \end{definition}

            \begin{definition}[AG Proximal Gradient Tri-Points Generic Form]
            \label{def:ag_prox_grad_tri_pt}
                With $h = f + g$, where $g$ is convex, $f$ is convex and $L$-Lipschitz smooth. 
                Define proximal gradient and gradient mapping operator 
                $$
                \begin{aligned}
                    \mathcal T_L(x) 
                    &:= \hprox_{L^{-1}g}(x - L^{-1}\nabla f(x)), 
                    \\
                    x^+ &= \mathcal T_L(x), 
                    \\
                    \mathcal G_L(x) 
                    &:= L(x -  x^+). 
                \end{aligned}
                $$
                Then the algorithm updates $(y_t, x_{t + 1}, z_{t + 1})$ with expression: 
                $$
                \begin{aligned}
                    y_t^+ &= \mathcal T_L(y_t)
                    \\
                    y_t &= (1 + L\eta_t)^{-1}(x_t + L\eta_t z_t)
                    \\
                    x_{t + 1} &= x_t - \tilde \eta \mathcal G_L(y_t)
                    \\
                    z_{t + 1} &= y_t - L^{-1}\mathcal G_L(y_t)
                \end{aligned}
                $$
                where the base case has $y_0 = x_0$. 
            \end{definition}
            \begin{remark}
                Observe that $z_{t + 1} = y_t^+$. 
            \end{remark}

            \begin{definition}[Tri-points Generic Form]\label{def:agg_tri}
                With $f$ be $L$-Lipschitz \\ 
                smooth and convex, choose any $y_0 = x_0=z_0$ and a non-negative sequence $\eta_t, \tilde\eta_t$, the algorithm admits form: 
                \begin{align*}
                    x_{t + 1} &= x_t - \tilde \eta_{t + 1} \nabla f(y_t) 
                    \\
                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t) 
                    \\
                    y_{t + 1} &= 
                    (1 + L\eta_{t + 1})^{-1}
                    (
                    x_{t + 1} + L\eta_{t + 1}z_{t + 1}
                    ). 
                \end{align*}
            \end{definition}
            \begin{remark}
                The parameter $\eta_t, \tilde\eta_{t + 1}$ are exactly the same as Ahn, Sra \cite[(6.24)]{ahn_understanding_2022}, but with the choice of $\mu = 0$. 
                This form is not explictly stated by Ahn and Sra but it's trivial to realize its presence regardless. 
                They are the same parameters for both algorithms and they are equivalent. 
                This will be proved in the coming parts. 
            \end{remark}
            \begin{definition}[Strongly Convex Tri-points Generic Form]
                \quad 
                With $f$ being $L$-Lipschitz smooth and $\mu > 0$ strongly convex then the Strongly convex Tri-Points generic form has updates of for iterates
                \begin{align*}
                    x_{t + 1} &= (1 + \mu\tilde \eta_{t + 1})^{-1}(x_t + \mu\tilde\eta_{t + 1}y_t^+), 
                    \\
                    z_{t + 1} &= y_t - L^{-1}\nabla f(y_t), 
                    \\
                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L\eta_{t + 1}z_{t +1}). 
                \end{align*}
            \end{definition}

        \subsubsection{Useful Observations about these Generic forms}
        \label{sec:AG_useful_information}

@@

            \begin{proposition}[Tri-points Strongly Convex Form via Ahn Sra 6.24]\label{prop:tri_scvx_from_ahn_sra_6.24}
                Coninue \\ 
                from \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with but with $\mu > 0$, under the same set of assumptions it recovers a tri-points algorithm with the following updates: 
                \begin{align*}
                    y_t^+ &= y_t - \mu^{-1}\nabla f(y_t)
                    \\
                    x_{t + 1} &= \argmin_{x} 
                    \left\lbrace
                        l_f (x; y_t) + \frac{\mu}{2} \Vert x - y_t\Vert^2 + 
                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2 
                    \right\rbrace
                    \\
                    &= \argmin_{x}
                    \left\lbrace
                        f(y_t) - \frac{1}{2\mu} \Vert \nabla f(y_t)\Vert^2 
                        + 
                        \frac{\mu
                        }{2}\Vert x - y_t^+\Vert^2
                        + 
                        \frac{1}{2\tilde \eta_{t + 1}}\Vert x - x_t\Vert^2
                    \right\rbrace
                    \\
                    &= (1 + \mu\tilde \eta_{t + 1})^{-1}
                    \left(
                        x_t + \mu \tilde \eta_{t + 1}y_t^{+}
                    \right)
                    \\
                    z_{t + 1} &= y_t - L^{-1} \nabla f(y_t)
                    \\
                    y_{t + 1} &= (1 + L\eta_{t + 1})^{-1}(x_{t + 1} + L \eta_{t + 1} z_{t + 1})
                \end{align*}
            \end{proposition}
            \begin{proof}
                By a similar argument made in the remarks of \hyperref[prop:tri_form_via_ppm]{proposition \ref*{prop:tri_form_via_ppm}} we have 
                \begin{align*}
                    l_f(x; y_t) + \frac{\mu}{2}\Vert x - y_t\Vert^2
                    &= 
                    f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
                    \\
                    \implies 
                    x_{t + 1} &= 
                    \argmin_{x} 
                    \left\lbrace
                        f(y_t) - \frac{1}{2\mu}\Vert \nabla f(y_t)\Vert^2 + \frac{\mu}{2}\Vert x - y_t^+\Vert^2
                        + 
                        \frac{1}{2\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
                    \right\rbrace
                    \\
                    &= 
                    \argmin_{x}
                    \left\lbrace
                        \frac{\mu}{2}\Vert x - y_t^+\Vert^2 + 
                        \frac{2}{\tilde \eta_{t + 1}} \Vert x - x_t\Vert^2
                    \right\rbrace
                    \\
                    &= (\mu + \tilde \eta_{t + 1})^{-1}
                    (\mu y_t^+ + \tilde \eta_{t + 1}x_t)
                    \\
                    &= (1 + \tilde \eta_{t + 1}\mu)^{-1}
                    (x_t + \mu\tilde \eta_{t + 1}y_t^+). 
                \end{align*}
                The updates for $y_{t + 1}, z_{t + 1}$ is the same as before because $\mu > 0$ only alters the update of the term $x_{t + 1}$ in \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}}. 
            \end{proof}

@@

            With $f$ having $L$-Lipschitz gradient and minimizer $x_*$, using 
            \hyperref[def:agg_ppm]{definition \ref*{def:agg_ppm}} with $\mu = 0$
            and 
            \hyperref[thm:ppm_descent_ineq]{theorem \ref*{thm:ppm_descent_ineq}} ,
            then we can derive the upper bounds for the RHS of the PPM descent inequality: 
                &= \tilde \eta_{t + 1} (f(z_{t + 1}) - f(x_*))

@@

        \begin{lemma}[Nonsmooth Generic AG Lyapunov Analysis]
        \label{lemma:nsmooth_agg_lyapunov_upper_bound}

@@

            In this remark we clarify the name ``similar triangule" as given in the literatures. 
